Hilbert space approximate Bayesian Gaussian processes using Stan

### 2020-03-24 Paper/manuscript_v2/manuscript_07_01.tex
author's list

\author{Gabriel R. Mayol$^{1*}$, Paul-Christian Bürkner$^{2}$, Michael R. Anderson$^3$, Aki Vehtari$^{2}$}

\date{
$^1$ TODO\break
$^2$ Department of Computer Science, Aalto University, Finland\break
$^3$ TODO\break
$^*$ Corresponding author, Email: gabriuma@gmail.com
}

@@

Due to the predictor \textit{sex} ($\bm{x}_2$) being a categorical variable ('1' for female and '2' for male), we apply dummy/treatment coding for the GP functions, in a similar way such coding is applied in linear models. A general mean GP function is defined for all observations, while a second GP function only applies to one of the predictor levels ('male' in this case) and is set to zero otherwise. More formally, this construction reads as follows:
%
\begin{align} 
f(\bm{x}) &\sim \mathcal{GP}(c + \bm{\beta}\bm{x}, k(\bm{x},\bm{x}', \theta_1)) + g(\bm{x}), \label{ch5_eq_gpml1}
\end{align}

@@

\noindent In the former equations, $\theta_1$ contains the hyperparameters $\alpha_1$ and $\ell_1$ which are the marginal variance and lengthscale, respectively, of the general mean GP function, and $\theta_2$ contains the hyperparameters $\alpha_2$ and $\ell_2$ which are the marginal variance and lengthscale, respectively, of a specific GP function restricted to the male sex ($\bm{x}_2=\text{'}2\text{'}$).

>>>>

\author{Gabriel Riutort-Mayol$^{1*}$, Michael R. Andersen$^2$, Paul-Christian Bürkner$^{3}$, Aki Vehtari$^{2}$}

\date{ \small
$^1$ Department of Cartographic Engineering, Geodesy, and Photogrammetry, Universitat Polit\`ecnica de Val\`encia, Spain. \break
$^2$ TODO\break
$^3$ Department of Computer Science, Aalto University, Finland\break
$^*$ Corresponding author, Email: gabriuma@gmail.com
}

@@

Due to the predictor \textit{sex} ($x_2$) being a categorical variable ('1' for female and '2' for male), we apply dummy/treatment coding for the GP functions, in a similar way such coding is applied in linear models. A general mean GP function is defined for all observations, while a second GP function only applies to one of the predictor levels ('male' in this case) and is set to zero otherwise. More formally, this construction reads as follows:
%
\begin{align} 
f(\bm{x}) &\sim \mathcal{GP}(c + \bm{\beta}\bm{x}, k(\bm{x},\bm{x}', \theta_1)) + g(\bm{x}), \label{ch5_eq_gpml1}
\end{align}

@@

\noindent In the former equations, $\theta_1$ contains the hyperparameters $\alpha_1$ and $\ell_1$ which are the marginal variance and lengthscale, respectively, of the general mean GP function, and $\theta_2$ contains the hyperparameters $\alpha_2$ and $\ell_2$ which are the marginal variance and lengthscale, respectively, of a specific GP function restricted to the male sex ($x_2=\text{'}2\text{'}$).
